%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Work \& Internship Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{D3.js, Python, Flask, git} % Job title
{Intelligent Big Data Visualisation Lab(iDVx), Tong Ji University} % Organization
{Research Assistant} % Location
{Sep. 2016 - Jun. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented a system provides Visual Analytics for Event Risk Prediction.}
\item { Provided interface for labeling events in multivariate time-series data, and heat-map based on visualization for displaying context-aware survival regression results. }
\item {Responsible for the system construction and visualization design. Co-worked with 2 teammates. }
\end{cvitems} 
}

\cventry
{D3.js, Python, Flask, git} % Job title
{Visualization Lab, New York University(Shanghai campus)} % Organization
{Research Assistant} % Location
{Jan. 2016 - Sep. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a new visual analytics system RCLens to support user-guided rare category exploration. Integrated the core LOFRCD algorithm with friendly user interface.}
\item {Responsible for the system construction and visualization design. Published an article on IEEE TVCG as first author.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{JavaScript, Html, CSS, git} % Job title
{ALM Group, Dept. of Software, Hewlett Packard Enterprise} % Organization
{Software Engineer Intern} % Location
{Jul.2015 - Jan.2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed the frontend of HP core product ALM  Octane  (a Software Development Life Cycle Management System), and ALM QoT (an SDLC management system on the mobile end).}
\end{cvitems}
}

%------------------------------------------------



%------------------------------------------------

\end{cventries}