%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}


%------------------------------------------------

\cventry
{Software Development Engineer, Java, C++, JNI, Android UI, Android NDK, Android Camera2, Neon, Metal, OpenGL} % Job title
{Adobe} % Organization
{San Jose, U.S.} % Location
{Feb. 2019 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
{\setlength\itemindent{-2ex} \item[] {Photoshop Camera - Launched on 2020 Adobe Max, mainly working on Android app.}}
\item[] {}
{\setlength\itemindent{-2ex} \item[] \textbf{UI/App Logic}}
\item {Edit in PsC. Enable user to import image from other app to edit in PsC. Implemented and refactored code on app navigation, activity launch mode. Handled various app state in background mode.}
\item {branch.io deeplink integration. Integrated branch.io SDK. Improved the code under extreme conditions like weak network, lens non-existence, iOS/Android lensID disparity.}
\item {Viewfinder dynamic layout. Mathematically calculated the geometry of the UI layout for various screen size and created transition animation.}
\item {Count down timer for capture picture/video. Added animation and defined UI behavior. Shutter sound for picture/video. Volume key shutter control.}
\item {Lens discover page asset local caching. C++ implementation for both iOS/Android app. Considered cache validation and update.}
\item {Lens bookmark. Integrated backend server bookmark capability. Design UI logic for both online, offline case.(Currently internal PoC)}
{\setlength\itemindent{-2ex} \item[] \textbf{Rendering Pipeline}}
\item {Panorama image as layer. Added 360 panorama image as new type of media layer, which works with existing mask capability like sky/salient mask. Add device orientation support with camera awareness. (Currently internal PoC)}
{\setlength\itemindent{-2ex} \item[] \textbf{Camera/Video}}
\item {Video recording. Coordinate resources like QE, designer, PM, iOS engineer to finalize feature expectations. Implemented the video frame processing feature to enable user record video with lens. (Currently under internal beta test.)}
\item {Camera2 API for exposure/focus/white balance control. Work with APIs like Camera Session, Capture Request, Camera Device Capability.}
{\setlength\itemindent{-2ex} \item[] \textbf{ML Inference Pipeline Acceleration}}
\item {Working on ARM Neon SIMD long register instruction set.}
\item {Performance tuning the DL implementation. Speed up code with techniques like computation caching, spatial locality, matrix transpose.}
\end{cvitems}
}




%------------------------------------------------

\cventry
{Software Development Intern, Spring Boot, Java, Microservice, MongoDB, Postman} % Job title
{Adobe} % Organization
{San Jose, U.S.} % Location
{Jun. 2018 - Nov. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Working on Adobe Campaign Spring Boot microservice. Wrote a scheduler to coordinate Spring instances on Ethos(Adobe microservice host platform).}
\item {Completed the test coverage with 8000+ lines of test codes. Introduce Project-Lombok to reduce redundancy in DTO code.}
\item {Implementing a Python microservice to serve Spark query jobs.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Development Intern, Django(Python), Ionic, Material Design, WeChat BE, HTML5, CSS} % Job title
{SAP} % Organization
{Shanghai, China} % Location
{Jun. 2016 - Nov. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Participated and organized the AI Assistant Over ERP innovation project. Helped designing the architecture of the system. Built the chart-rendering component and helped integrating the NLP engine with SAP Anywhere ERP system.}
\item {Organized the “Come and Code” Programming Share Talk. Presented Motion Graphics and Processing Programming.}
\item {Prototyped two POCs of Team-building System and BuyItTogether app using Django Restful, Angular.js, and Material Design.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Android Development Intern, Android(Java), AndroidStudio} % Job title
{GLow Inc.} % Organization
{Shanghai, China} % Location
{Jan. 2016 - Mar. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented customized promotion card UI widgets for Baby app under supervision. Added loggings function for the app.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Development Intern, Django(Python), Nodejs, MySQL, HTML5, CSS} % Job title
{Ericsson} % Organization
{Shanghai, China} % Location
{Mar. 2015 - Dec. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Completed PoC for Network Slicing based on Node.js WebSocket communication.}
\item {Implemented WPST Log Visualization System using Django with MySQL DB, which supported editing and inquiring.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
