%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Project Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Django(Python), Apache, PostgreSQL, MaterializeCSS} % Job title
{McGill Univ. Physics Online Quiz Website} % Organization
{Shanghai, China} % Location
{Mar. 2017 - Jun. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed, implemented and deployed a complete online quiz website for McGill University Physics Department, powering a 500-student class.}
\item {Deployed the whole website on VPS with Apache and PostgreSQL as the http-server and database. This was a personal project as well as the undergraduate thesis for my CS degree.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Android(Java), AndroidStudio, AMap plugin} % Job title
{TrackLabel, Android App} % Organization
{Shanghai, China} % Location
{Mar. 2016 - Jun. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Wrote a complete Android App. Implemented Bluetooth communication feature that scanned the paired devices and found a missing nearby smart phone by ringing through Bluetooth control.}
\item {Integrated fully-functioning AMap API with GPS location. The app can record last Bluetooth detected locations for paired devices, which helps users to find missing devices. Followed best practices in Android Marshmallow with standard Google Material Design UI.}
\end{cvitems}
}

%------------------------------------------------

% \cventry
% {Angular.js, HTML5, CSS} % Job title
% {GE AWS Cloud Control, Web UI Prototype} % Organization
% {Shanghai, China} % Location
% {Jan. 2016 - Feb. 2016} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Applied Grunt-built yeoman Angular.js framework. Created customized UI widgets and responsive CSS animation.}
% \item {Implemented two-way binding of Angular.js for rendering policy instead of traditional JQuery way, which effectively improved the performance.}
% \end{cvitems}
% }

%------------------------------------------------

\end{cventries}
